---
title: "Homework 11"
author: "Kimberly McNeil"
date: "4/18/2026"
output:
  html_document:
    code_folding: hide
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning=FALSE, 
  message=FALSE
  )
library(knitr)
library(dplyr)
library(tidyverse)
library(nycflights13)
library(maps)
```

# NYC Flights Data

Let's make a map of flights out of New York City in 2013.

## Frequencies of Origin/Destination Pairs

The following table showcases the first six frequencies of all origin/destination pairs:^[Question 1 Complete]
```{r}
freq_tab = flights %>%
  count(origin, dest)

kable(head(freq_tab), caption = "First Six Frequencies of all Origin/Destination Pairs")
```

## Origin Latitude and Longitude

The following table showcases the first six rows of the previous frequency table with the origin's latitude and longitude added in:^[Question 2 Complete]

```{r}
freq_tab_org = freq_tab %>%
  left_join(
    airports %>% select(faa, lat, lon),
    join_by(origin == faa)) %>%
  rename(origin_lat = lat, origin_lon = lon) %>%
  relocate(origin_lat, origin_lon, .after = origin)

kable(head(freq_tab_org), caption = "First Six Rows of the Frequency Table with Origin's Lat/Lon")
```

## Destination Latitude Longitude

The following table showcases the first six rows of the previous frequency table with both the origin's latitude and longitude added in:^[Question 3 Complete]

```{r}
freq_tab_dest = freq_tab_org %>%
  left_join(
    airports %>% select(faa, lat, lon),
    join_by(dest == faa)) %>%
  rename(dest_lat = lat, dest_lon = lon) %>%
  relocate(dest_lat, dest_lon, .after = dest)

kable(head(freq_tab_dest), caption = "First Six Rows of the Frequency Table with both Origin and Dest's Lat/Lon")
```

# Map of the U.S.A

The following image shows a map of the continental United States:^[Question 4 Complete]

```{r}
ggplot() +
  geom_polygon(
    data = map_data("state") ,
    mapping = aes(x = long, y = lat, group = group),
    fill = NA, color = "gray"
    ) +
  coord_fixed(1.3)
```

## U.S. Map with Flight Lines

Now, let's look at our U.S. map with lines from each origin to each destination, with transparency mapped to the frequency of that origin-destination pair:^[Question 5 Complete]

```{r}
ggplot() +
  geom_polygon(
    data = map_data("state"),
    aes(x = long, y = lat, group = group),
    fill = NA, color = "gray"
  ) +
  geom_segment(
    data = freq_tab_dest,
    aes(
      x = origin_lon,
      y = origin_lat,
      xend = dest_lon,
      yend = dest_lat,
      alpha = n
    ),
    color = "blue"
  ) +
  coord_fixed(1.3)
```

## U.S. Map with Flight Lines (only within the U.S.)

Some of those flights left the U.S., so let's look at only the ones contained in the U.S.^[Question 6 Complete]

```{r}
freq_tab_us = freq_tab_dest %>%
  filter(
    dest_lon > -125, dest_lon < -66,
    dest_lat > 25,  dest_lat < 50
  )

ggplot() +
  geom_polygon(
    data = map_data("state"),
    aes(x = long, y = lat, group = group),
    fill = NA, color = "gray"
  ) +
  geom_segment(
    data = freq_tab_us,
    aes(
      x = origin_lon,
      y = origin_lat,
      xend = dest_lon,
      yend = dest_lat,
      alpha = n
    ),
    color = "blue"
  ) +
  coord_fixed(1.3)
```
